Decoding Sleep Disorders Through Self-Reported Patterns

### 2024-04-13 paper/paper.qmd
added sample data

The survey participants' ages range widely, reflecting the diversity of the American population. Variables are finely tuned to capture the multifaceted nature of sleep, encompassing aspects such as duration, disruptions, and subjective experiences of daytime sleepiness. The NHANES protocol ensures that this dataset is a robust and reliable source of information, adhering to stringent ethical standards and data collection methods, as detailed in the NHANES Analytic Guidelines. For further information on the data cleaning specifics and validation checks, please see the supplementary material in @sec-appendix (Appendix).

@@

**Daytime Sleepiness (SLQ120)**: This variable assesses how often respondents feel excessively or overly sleepy during the day, with values ranging from 0 (Never) to 4 (Almost always). It is an indicator of sleep quality and quantity, as well as potential sleep disorders.

@@

@@

@@

# Appendix {.unnumbered #sec-appendix}

## Additional Data Details

## Model Details {#sec-model-details}

>>>>

The survey participants' ages range widely, reflecting the diversity of the American population. Variables are finely tuned to capture the multifaceted nature of sleep, encompassing aspects such as duration, disruptions, and subjective experiences of daytime sleepiness. The NHANES protocol ensures that this dataset is a robust and reliable source of information, adhering to stringent ethical standards and data collection methods, as detailed in the NHANES Analytic Guidelines. For further information on the data cleaning specifics and validation checks, please see the supplementary material in @sec-add-data.

@@

**Overly Sleep Frequency (SLQ120)**: This variable assesses how often respondents feel excessively or overly sleepy during the day, with values ranging from 0 (Never) to 4 (Almost always). It is an indicator of sleep quality and quantity, as well as potential sleep disorders.

@@

## Sample of Cleaned Sleep Disorder Data

```{r}
#| label: tbl-sleep-data-sample
#| tbl-cap: Sample of Sleep Disorder Data
#| echo: false
# Code created with the help from ChatGPT
sample_data <- head(cleaned_data) %>%
  select(RespondentID, WeekdaySleepDuration, WeekendSleepDuration, SnoringFrequency, BreathingPauseFrequency, OverlySleepFrequency, ReportedSleepTrouble)

# Create a nicely formatted table with custom column names
kable(sample_data, col.names = c("Respondent ID", "Weekday Sleep Duration (hrs)", "Weekend Sleep Duration (hrs)", "Snoring Frequency", "Breathing Pause Frequency", "Overly Sleep Frequency", "Reported Sleep Trouble"))

```

@tbl-sleep-data-sample represents a subset of the broader NHANES sleep disorder dataset. Each row in the table corresponds to an individual participant, uniquely identified by their Respondent ID. The "Weekday Sleep Duration (hrs)" and "Weekend Sleep Duration (hrs)" columns quantify the number of hours slept during the weekdays and weekends, respectively, providing a snapshot of the individual's sleep patterns. "Snoring Frequency" and "Breathing Pause Frequency" are categorical measures that reflect how often the respondents experience snoring and breathing pauses during sleep, common indicators of sleep disturbances such as sleep apnea. The "Overly Sleep Frequency" column indicates the frequency at which respondents report feeling overly sleepy during the day, a sign that can be indicative of inadequate sleep quality or quantity. Lastly, the "Reported Sleep Trouble" column is a binary measure showing whether the respondent has reported having sleep troubles to a health professional, with 0 signifying no reported trouble and 1 indicating reported trouble.

@@

## Data Exploration: {#sec-exploration}

@@

# Appendix {#sec-appendix}

## Additional Data Details {#sec-add-data}

## Model Details
